%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
 
\documentclass[a4paper]{resume} % Use the custom resume.cls style 

\usepackage[left=0.3 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Florian GROLLEAU}
\address{2 rue Louis Blériot - 78960 - Voisins-le-Bretonneux, Yvelines, France}
\address{+33 07 81 00 75 53 - f.grolleau@netc.fr - 
4\textsuperscript{th}-year student (Master’s level, M1) - 
\href{https://www.linkedin.com/in/florian-grolleau-3a7a22274}{LinkedIn}}
\usepackage[hidelinks]{hyperref}



\begin{document}  

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf \href{https://www.sciencespo-saintgermainenlaye.fr/en/}{SCIENCES PO Saint-Germain-en-Laye - Master’s in Political Science}} \hfill {09/2022 - Present}
\\
Social Sciences, Data Analysis, International Relations, Economics.
\\
Digital Humanities, Sustainability, Policy Analysis, Governance.

{\bf \href{https://cytech.cyu.fr/}{Cergy-Paris University - Master’s Degree in Engineering - Data Science}} \hfill {09/2022 - Present}
\\ 
 \textit{Dual Degree with Sciences Po at CY Tech}
\\
Data Science, AI-Machine Learning (scikitlearn, pandas, keras, numpy - SQL, Java).
\\
Statistics (Regression models, Statistical tests, plotly, seaborn - R, MatLab, MongoDB, QGis).

{\bf \href{https://www.uib.no/en}{University of Bergen, Norway - Erasmus Academic Exchange - 6 months}} \hfill {01/2025 - 06/2025}
\\
Indigenous Rights, Russian Politics, Comparative Analysis of Latin American Regimes.
\end{rSection} 
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

%	INTERNSHIP/TRAININGS 
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

{\bf \href{https://www.linkedin.com/company/commandement-pour-l-afrique-cpa/posts/?feedView=all}{Intern - French Ministry of Armed Forces - Libreville, Gabon - 5 months}} \hfill {04/2026 - 08/2026}
\\Monitoring and analysis within France’s Area of Permanent Responsibility in Central Africa.
\\Assigned to the Joint Liaison Detachment (DLIA-G) and the Influence and Information Warfare Office (ILI).
\\Development of a \textbf{\href{https://github.com/Flor5378/-ENG-GlobalRiskIntelligencePlatform}{Predictive Dashboard}} on socio-economic issues in Gabon and the DRC (88\% accuracy).

{\bf \href{https://www.linkedin.com/company/bureau-analyse-des-enjeux-de-la-d%C3%A9fense/?viewAsMember=true}{Partnership Manager - Office for the Analysis of Defense Issues (Association) }} \hfill{04/2025 - Present}
\\
150+ members, Partnerships and MILIPOL 2025; supported ceremonial events military authorities; drafted brief military reports.

{\bf Volunteer - Bear Sanctuary, Croatia, Kuterevo} \hfill {08/2025}
\\
Bear care and sanctuary maintenance, manual work and enclosure upkeep.

{\bf \href{https://www.linkedin.com/company/anfsi/about/en/}{ANFSI Intern - French Digital Agency of Internal Security Forces - 1 month}} \hfill {07/2025}
\\
Improvement of drone databases over trajectories, coordinates, and identifiers with PostgreSQL / MongoDB.
\\Classification Model (Hybrid KNN, Random Forest, and XGBoost, Achieving 90\% Accuracy).

{\bf {MUN Saint-Germain (Association) - Treasurer}} \hfill {09/2023 - 12/2024}
\\(100+ members), managed budget and finances, financial reporting, managed social media (2500+ followers).

\end{rSection}  

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }  
Data Science & Python (keras,
scikitlearn, ArcPy, ArcGIS, BeautifulSoup, Geopandas), Java, R, Js - React.\\& HTML-CSS, LaTeX, Talend, Bash, Powershell, SQL, Docker, JavaFX, MongoDB, NLP.\\
Social Sciences & Geographic focus - Central-East Africa Coast, Western Europe, Scandinavia
\\& International Relations, Scientific Monitoring, Public Policy Analysis.\\& Data visualization, Power BI, Statistics, Microsoft
Office Suite.
\\
Languages & French - Native \textbar{} English - C1/Fluent \textbar{} German - B2/Intermediate
\end{tabular}   

\end{rSection}


%-------------------------------------------------------------------------------
%	PROJECTS

\begin{rSection}{Academic Projects\makebox[400pt][r]{\scriptsize available here: \href{https://github.com/Flor5378}{github.com/Flor5378}}}

\begin{tabular}{ @{} l @{\hspace{4ex}} l @{} }

\textbf{Social Sciences} & \textbf{Data Science} \\


\href{https://github.com/Flor5378/-ENG-Modern-Warfare-UAVs-and-Ethics}{[EN] Modern Warfare UAVs and Ethics} &
\href{https://github.com/Flor5378/-FR-ENG-DroneClassificationUA}{[EN-FR] Drone Classification in Ukraine} \\

\href{https://github.com/Flor5378/-ENG-DigitalDemocracyEssay}{[EN] Private Companies and US Immigration Policies} &
\href{https://github.com/Flor5378/-ENG-AirQualityIndexStudies}{[EN] Air Quality Index Studies} \\

\href{https://github.com/Flor5378/-FR-Data_and_Territories}{[FR] Data and Territories Challenge} &
\href{https://github.com/Flor5378/-ENG-DronesDetectionFrenchTerritory}{[FR] Drone Detection over French Territory} \\

\href{https://github.com/Flor5378/-FR-FormationsenLigneStatistiques}{[FR] Online Courses and Success Rate} &
\href{https://github.com/Flor5378/-FR-RequetesSQLetOptimisationBDD}{[FR] SQL Queries and Optimization} \\

\href{https://github.com/Flor5378/-FR-MarchesPredictifs_ConcurrenceInformationnelle}{[FR] Predictive Markets and Information Competition} &
\href{https://github.com/Flor5378/-FR-ENG-SortingAlgorithmsinPython}{[FR] Sorting Algorithms in Python} \\

\end{tabular}

\end{rSection}

\begin{rSection}{Interests}

Regular reader of peer-reviewed journals (economics, defense, aerospace) and institutional infographics (Passé Composé, CNRS). Educational travel focused on cultural, historical, and environmental insights. Sports: handball (6y), table tennis (10y), mountain biking (7y). Semi-professional RTS player (Age of Empires II, 2200 Elo, Top 150 worldwide).

\end{rSection}

\end{document}
